Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2016-07-09 inst/examples/20160715-slides-Krakow.Rmd
ok

library(stringr)
library(dplyr)
library(tidyr)
library(reshape2)
library(ggplot2)
library(bibliographica)
library(fennica)
library(sorvi)
library(devtools)
# install_github("ropengov/gisfin")
# devtools::install_github('cttobin/ggthemr')
library(gisfin)
library(ggthemr)

@@

# Nice default themes
# https://github.com/cttobin/ggthemr#palettes
#ggthemr('fresh', text_size = 20)
# ggthemr('greyscale', text_size = 20)
#ggthemr('light', text_size = 20)
# ggthemr('pale', text_size = 20)
ggthemr_reset() # Reset theme
```

>>>>

library(stringr)
library(dplyr)
library(tidyr)
library(reshape2)
library(ggplot2)
library(bibliographica)
library(fennica)
library(sorvi)
library(devtools)
# install_github("ropengov/gisfin")
# devtools::install_github('cttobin/ggthemr')
library(gisfin)
#library(ggthemr)

@@

# Nice default themes
# https://github.com/cttobin/ggthemr#palettes
#ggthemr('fresh', text_size = 20)
# ggthemr('greyscale', text_size = 20)
#ggthemr('light', text_size = 20)
# ggthemr('pale', text_size = 20)
#ggthemr_reset() # Reset theme
```
